Learning how to act: making good decisions with machine learning

### 2017-10-20 thesis/abstract.tex
finalised talk, replaced most instances of the word framework, fixed spelling and repeated word errors, completes aknowledgements.

The goal of this thesis to connect and unify these key approaches. I introduce causal bandit problems: a framework that combines causal graphical models, which were developed for observational causal inference, with multi-armed bandit problems, which are a subset of reinforcement learning problems that are simple enough to admit formal analysis. I show that knowledge of the causal structure allows us to transfer information learned about the outcome of one action to predict the outcome of an alternate action, yielding a novel form of structure between bandit arms that cannot be exploited by existing algorithms. I propose an algorithm for causal bandit problems and prove bounds on the simple regret demonstrating it is close to mini-max optimal and strictly better than algorithms that do not use the additional causal information.

>>>>

The goal of this thesis to connect and unify these key approaches. I introduce causal bandit problems: a synthesis that combines causal graphical models, which were developed for observational causal inference, with multi-armed bandit problems, which are a subset of reinforcement learning problems that are simple enough to admit formal analysis. I show that knowledge of the causal structure allows us to transfer information learned about the outcome of one action to predict the outcome of an alternate action, yielding a novel form of structure between bandit arms that cannot be exploited by existing algorithms. I propose an algorithm for causal bandit problems and prove bounds on the simple regret demonstrating it is close to mini-max optimal and better than algorithms that do not use the additional causal information.

### 2017-10-20 thesis/offcuts.tex
finalised talk, replaced most instances of the word framework, fixed spelling and repeated word errors, completes aknowledgements.

>>>>

 \chapter{Causation vs Prediction}

 Mixing continuous experimentation at an individual level with batch approaches. There may be fixed costs associated with \quotes{enabling} certain actions. For example, social programs may have some fixed overheads, no matter how many people are enrolled in them, etc. Reuse data obtained to optimise for one outcome to learn about optimising for another. We don't have a single outcome or loss-measure that fully incorporates everything we care about for the majority of problems.

 The two cultures \citep{Breiman2001}
 - wrong because suggests we can just use the machine learning approach for everything. Does not address the problems that a) structural assumptions required for causal inference. b) we cannot use cross-validation to assess the validity of a causal model (really b is the whole point).

 To explain or to predict \citep{Shmueli2010}
 - wrong because they assume all the parts of explanatory modelling are required - so black box models cannot be used.

 Predict the relationship between X and Y as a way to stratify to reduce the variance in an experiment.

 They consider a different definition of explanatory models,

 Definition as backwards. Explanatory models focus on theory because some theory (or equivalently stated assumptions) are required in order to predict the outcome of an intervention from observational data.

 Causal modelling frameworks allow us to separate assumptions about the structure of the relationships between variables from assumptions about the functional form.

 What can be data driven and what cannot? (for a given set of assumptions).

 Allowing for the possibility that we might only need to be able to predict the outcome of an intervention on a given subset of variables (for example those over which we have the ability to manipulate) or the possibility that we can can obtain observation from directly intervening in a system creates creates a need for models that are neither explanatory or predictive in the language of EoP but are built on a hybrid of both approaches.
